### 2021-04-01 Chapter-3/Chapter-3.tex
Updates from Overleaf

If the input sensitive data can affect the control flow of the victim program, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the input values. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} does not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then can attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. As a result, the sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.  Figure~\ref{fig:chapter3:cf}(b) shows an opposite situation. While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.

\subsection{Data Flow}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x7f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(a)}

>>>>

If the input sensitive data can affect the control flow of the victim program, then an attacker can infer the sensitive data by observing the control flow during the execution. Figure~\ref{fig:chapter3:cf}(a) shows such an example. The function takes a public value \textsf{m} and a secret \textsf{k} as the input values. The code at line 2 ensures that the lower 7 bits of the value \textsf{k} does not affect the value \textsf{b}. However, depending on the value of \text{m}, the code snippet in Figure~\ref{fig:chapter3:cf}(a) may have a leakage site. If the eighth bit of \textsf{m} is 1, then can attacker can also infer the eighth bit of \textsf{k} by observing the branch at line 4 or line 6. The right figure shows the corresponding machine code. It has a conditional jump instruction \textsf{jne}. The sensitive input \textsf{k} can affects the program counter (the rip register), which is the root cause of the side-channel leakages.  Figure~\ref{fig:chapter3:cf}(b) shows a different situation. While the sensitive input \textsf{k} can affect the if else branch, the compiler removes the branch with a conditional set instruction.  The opposite situation is the same. For example, recent work tries to  use bit masking to rewrite the program with control flows. However, for some situations~\cite{Coppens:2009:PMT:1607723.1608124}, compilers (e.g., GCC) optimize the code too much (from a security view) and remove the unnecessary copy by reintroducing conditional moves.
\subsection{Data Flow}
\begin{figure}[h]
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.0\textwidth, frame=none]
uint8_t T[128];
...
int example3(uint8_t secret){
  uint32_t index = 0;
  index = (index + secret) % 128;
  uint8_t t = T[index];
  ...
}
\end{lstlisting}
\end{minipage}
\hfill
\begin{minipage}{0.4\linewidth}
\begin{lstlisting}[xleftmargin=.0\textwidth, xrightmargin=.00\textwidth, frame=none, numbers=none, mathescape=true]
...
lea    edx, [addr_T]
mov    eax, [addr_secret]
and    eax, 0x7f
movzx  eax, [addr_T + eax*1]
...
\end{lstlisting}
\end{minipage}\caption*{(a)}
